

%%% Choose a language %%%

\newif\ifEN
% \ENtrue   % uncomment this for english
\ENfalse   % uncomment this for czech

%%% Configuration of the title page %%%

\def\ThesisTitleStyle{mff} % MFF style
%\def\ThesisTitleStyle{cuni} % uncomment for old-style with cuni.cz logo
%\def\ThesisTitleStyle{natur} % uncomment for nature faculty logo

\def\UKFaculty{Faculty of Mathematics and Physics}
%\def\UKFaculty{Faculty of Science}

\def\UKName{Charles University in Prague} % this is not used in the "mff" style

% Thesis type names, as used in several places in the title
\def\ThesisTypeTitle{\ifEN BACHELOR THESIS \else BAKALÁŘSKÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN MASTER THESIS \else DIPLOMOVÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN RIGOROUS THESIS \else RIGORÓZNÍ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN DOCTORAL THESIS \else DISERTAČNÍ PRÁCE \fi}
\def\ThesisGenitive{\ifEN bachelor \else bakalářské \fi}
%\def\ThesisGenitive{\ifEN master \else diplomové \fi}
%\def\ThesisGenitive{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisGenitive{\ifEN doctoral \else disertační \fi}
\def\ThesisAccusative{\ifEN bachelor \else bakalářskou \fi}
%\def\ThesisAccusative{\ifEN master \else diplomovou \fi}
%\def\ThesisAccusative{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisAccusative{\ifEN doctoral \else disertační \fi}



%%% Fill in your details %%%

% (Note: \xxx is a "ToDo label" which makes the unfilled visible. Remove it.)
\def\ThesisTitle{Nástroj pro průzkum a vizualizaci modelu pro simulátor mozku Mozaik}
\def\ThesisAuthor{Filip Ježek}
\def\YearSubmitted{2023}

% department assigned to the thesis
\def\Department{Katedra softwaru a výuky informatiky}
% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Katedra}

\def\Supervisor{Mgr. Ján Antolík, Ph.D.}
\def\SupervisorsDepartment{Katedra softwaru a výuky informatiky}

% Study programme and specialization
\def\StudyProgramme{Informatika}
\def\StudyBranch{Databáze a web}

\def\Dedication{%
Dedication. \xxx{It is nice to say thanks to supervisors, friends, family, book authors and food providers.}
}

\def\AbstractEN{%
Simulations of biological neural networks are an important tool for understanding how the brain processes information. Mozaik is a workflow framework that allows such simulations to be created, run and analyzed. Currently, however, there is no easy way to visualize in it either the network or the data structures created by individual analyses. This work is a web application that allows users to visualize networks and data structures stored in datastores for individual simulations. The given visualizations can be searched using complex queries, interactively examined and compared with each other. This makes the work of researchers working with the Mozaik framework much more efficient.
% ABSTRACT IS NOT A COPY OF YOUR THESIS ASSIGNMENT!
}

\def\AbstractCS{%
Simulace biologických neuronových sítí jsou důležitým nástrojem pro porozumění tomu, jak mozek zpracovává informace. Mozaik je workflow framework, který umožňuje takové simulace vytvářet, spouštět a analyzovat. V~současné době ale neexistuje snadný způsob, jak v~něm vizualizovat ani síť, ani datové struktury vytvořené jednotlivými analýzami. Tato práce je webová aplikace, která umožňuje vizualizovat sítě a~datové struktury uložené v datastorech pro jednotlivé simulace. Dané vizualizace lze vyhledávat pomocí komplexních dotazů, interaktivně je zkoumat a~vzájemně mezi sebou srovnávat. To výrazně zefektivňuje práci výzkumníků, kteří s~frameworkem Mozaik zacházejí.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces.
% Keywords are useful for indexing and searching for the theses by topic.
\def\Keywords{%
{vizualizace} {webová aplikace} {model mozku}
}

% If your abstracts are long and do not fit in the infopage, you can make the
% fonts a bit smaller by this setting. (Also, you should try to compress your abstract more.)
% Alternatively, consider increasing the size of the page by uncommenting the
% geometry modification in thesis.tex.
\def\InfoPageFont{}
%\def\InfoPageFont{\small}  %uncomment to decrease font size

\ifEN\relax\else
% If you are writing a czech thesis, you additionally need to fill in the
% english translation of the metadata here!
\def\ThesisTitleEN{A model inspection/visualization tool for brain simulation framework}
\def\DepartmentEN{Department of Software and Computer Science Education}
\def\DeptTypeEN{Department}
\def\SupervisorsDepartmentEN{Department of Software and Computer Science Education}
\def\StudyProgrammeEN{Computer Science}
\def\StudyBranchEN{Databases and Web}
\def\KeywordsEN{%
{visualization} {web application} {brain model}
}
\fi
